\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-09 doc/paper.tex
doc/paper.tex: trim optional trailing / from links

\fs can be downloaded from \url{http://flexiblesusy.hepforge.org}.  To
create a custom spectrum generator the following requirements are
necessary:
%
\begin{itemize}
\item \mathematica, version 7 or higher
\item SARAH, version 4.0.4 or higher \url{http://sarah.hepforge.org}
\item C++11 compatible compiler (g++ 4.4.7 or higher, clang++ 3.1 or
  higher, icpc 12.1 or higher)
\item FORTRAN compiler (gfortran, ifort etc.)
\item Eigen library, version 3.1 or higher
  \url{http://eigen.tuxfamily.org}
\item Boost library, version 1.36.0 or higher
  \url{http://www.boost.org}
\item GNU scientific library \url{http://www.gnu.org/software/gsl/}
\item an implementation of LAPACK \url{http://www.netlib.org/lapack/}
  such as ATLAS \url{http://math-atlas.sourceforge.net/} or
  Intel Math Kernel Library \url{http://software.intel.com/intel-mkl}
\end{itemize}
%
Optional:
%
\begin{itemize}
\item Looptools, version 2.8 or higher
  \url{http://www.feynarts.de/looptools/}
\end{itemize}

@@

\fs can be downloaded as a gzipped tar file from
\url{http://flexiblesusy.hepforge.org/}.  To download and install
version 1.0.0 run:
%
\begin{lstlisting}[language=bash]
$ wget https://www.hepforge.org/archive/flexiblesusy/FlexibleSUSY-1.0.0.tar.gz
$ tar -xf FlexibleSUSY-1.0.0.tar.gz
$ cd FlexibleSUSY-1.0.0/
\end{lstlisting}%% $
%
A CMSSM spectrum generator can be created with the following three
commands:
%
\begin{lstlisting}[language=bash]
$ ./createmodel --name=MSSM
$ ./configure --with-models=MSSM
$ make
\end{lstlisting}%% $
%
The first command creates the model directory \code{models/MSSM/}
together with a CMSSM model file.  The \code{configure} script checks
the system requirements and creates the \code{Makefile}.  See
\code{./configure --help} for more options.  Executing \code{make}
will start \mathematica to generate the spectrum generator and compile
it.  The resulting executable can be run like this:
%
\begin{lstlisting}[language=bash]
$ models/MSSM/run_MSSM.x --slha-input-file=model_files/MSSM/LesHouches.in.MSSM
\end{lstlisting}%% $
%
When executed, the spectrum generator tries to find a set of \DRbar\
model parameters consistent with all CMSSM boundary conditions for the
parameter point given in the SLHA input file
\code{model_files/MSSM/LesHouches.in.MSSM}.  Afterwards, the pole mass
spectrum and mixing matrices are calculated and written to the command
line in SLHA format \cite{Skands:2003cj,Allanach:2008qq}.  For the
parameter point given in the above example the calculated pole mass
spectrum reads
%
\begin{lstlisting}
Block MASS
   1000021     1.15236966E+03   # Glu
   1000024     3.85774334E+02   # Cha_1
   1000037     6.50460073E+02   # Cha_2
        25     1.14766149E+02   # hh_1
        35     7.06792640E+02   # hh_2
        37     7.11388516E+02   # Hpm_2
        36     7.06523105E+02   # Ah_2
   1000012     3.51856376E+02   # Sv_1
   1000014     3.53042556E+02   # Sv_2
   1000016     3.53046504E+02   # Sv_3
   1000022     2.03889780E+02   # Chi_1
   1000023     3.85760714E+02   # Chi_2
   1000025     6.36544884E+02   # Chi_3
   1000035     6.50133768E+02   # Chi_4
   1000001     9.66656018E+02   # Sd_1
   1000003     1.00983181E+03   # Sd_2
   1000005     1.01651873E+03   # Sd_3
   2000001     1.01653005E+03   # Sd_4
   2000003     1.06089534E+03   # Sd_5
   2000005     1.06090238E+03   # Sd_6
   1000011     2.22570305E+02   # Se_1
   1000013     2.29864536E+02   # Se_2
   1000015     2.29888846E+02   # Se_3
   2000011     3.61946671E+02   # Se_4
   2000013     3.61950866E+02   # Se_5
   2000015     3.63136031E+02   # Se_6
   1000002     8.09787818E+02   # Su_1
   1000004     1.01454197E+03   # Su_2
   1000006     1.01981109E+03   # Su_3
   2000002     1.02015269E+03   # Su_4
   2000004     1.05807759E+03   # Su_5
   2000006     1.05808168E+03   # Su_6
\end{lstlisting}

>>>>

\fs can be downloaded from \url{http://flexiblesusy.hepforge.org}.  To
create a custom spectrum generator the following requirements are
necessary:
%
\begin{itemize}
\item \mathematica, version 7 or higher
\item SARAH, version 4.0.4 or higher \url{http://sarah.hepforge.org}
\item C++11 compatible compiler (g++ 4.4.7 or higher, clang++ 3.1 or
  higher, icpc 12.1 or higher)
\item FORTRAN compiler (gfortran, ifort etc.)
\item Eigen library, version 3.1 or higher
  \url{http://eigen.tuxfamily.org}
\item Boost library, version 1.36.0 or higher
  \url{http://www.boost.org}
\item GNU scientific library \url{http://www.gnu.org/software/gsl}
\item an implementation of LAPACK \url{http://www.netlib.org/lapack}
  such as ATLAS \url{http://math-atlas.sourceforge.net} or
  Intel Math Kernel Library \url{http://software.intel.com/intel-mkl}
\end{itemize}
%
Optional:
%
\begin{itemize}
\item Looptools, version 2.8 or higher
  \url{http://www.feynarts.de/looptools}
\end{itemize}

@@

\fs can be downloaded as a gzipped tar file from
\url{http://flexiblesusy.hepforge.org}.  To download and install
version 1.0.0 run:
%
\begin{lstlisting}[language=bash]
$ wget https://www.hepforge.org/archive/flexiblesusy/FlexibleSUSY-1.0.0.tar.gz
$ tar -xf FlexibleSUSY-1.0.0.tar.gz
$ cd FlexibleSUSY-1.0.0/
\end{lstlisting}%% $
%
A CMSSM spectrum generator can be created with the following three
commands:
%
\begin{lstlisting}[language=bash]
$ ./createmodel --name=MSSM
$ ./configure --with-models=MSSM
$ make
\end{lstlisting}%% $
%
The first command creates the model directory \code{models/MSSM/}
together with a CMSSM model file.  The \code{configure} script checks
the system requirements and creates the \code{Makefile}.  See
\code{./configure --help} for more options.  Executing \code{make}
will start \mathematica to generate the spectrum generator and compile
it.  The resulting executable can be run like this:
%
\begin{lstlisting}[language=bash]
$ models/MSSM/run_MSSM.x --slha-input-file=model_files/MSSM/LesHouches.in.MSSM
\end{lstlisting}%% $
%
When executed, the spectrum generator tries to find a set of \DRbar\
model parameters consistent with all CMSSM boundary conditions for the
parameter point given in the SLHA input file
\code{model_files/MSSM/LesHouches.in.MSSM}.  Afterwards, the pole mass
spectrum and mixing matrices are calculated and written to the command
line in SLHA format \cite{Skands:2003cj,Allanach:2008qq}.  For the
parameter point given in the above example the calculated pole mass
spectrum reads
%
\begin{lstlisting}
Block MASS
   1000021     1.15236966E+03   # Glu
   1000024     3.85774334E+02   # Cha_1
   1000037     6.50460073E+02   # Cha_2
        25     1.14766149E+02   # hh_1
        35     7.06792640E+02   # hh_2
        37     7.11388516E+02   # Hpm_2
        36     7.06523105E+02   # Ah_2
   1000012     3.51856376E+02   # Sv_1
   1000014     3.53042556E+02   # Sv_2
   1000016     3.53046504E+02   # Sv_3
   1000022     2.03889780E+02   # Chi_1
   1000023     3.85760714E+02   # Chi_2
   1000025     6.36544884E+02   # Chi_3
   1000035     6.50133768E+02   # Chi_4
   1000001     9.66656018E+02   # Sd_1
   1000003     1.00983181E+03   # Sd_2
   1000005     1.01651873E+03   # Sd_3
   2000001     1.01653005E+03   # Sd_4
   2000003     1.06089534E+03   # Sd_5
   2000005     1.06090238E+03   # Sd_6
   1000011     2.22570305E+02   # Se_1
   1000013     2.29864536E+02   # Se_2
   1000015     2.29888846E+02   # Se_3
   2000011     3.61946671E+02   # Se_4
   2000013     3.61950866E+02   # Se_5
   2000015     3.63136031E+02   # Se_6
   1000002     8.09787818E+02   # Su_1
   1000004     1.01454197E+03   # Su_2
   1000006     1.01981109E+03   # Su_3
   2000002     1.02015269E+03   # Su_4
   2000004     1.05807759E+03   # Su_5
   2000006     1.05808168E+03   # Su_6
\end{lstlisting}
